### 2012-01-26 trunk/GUIErrorDetector/paper/evaluation.tex
revise

We use a set of open-source projects from Sourceforge, Google code and Eclipse plugin
market as evaluation subjects. To choose subjects for each supported GUI framework,
we first search the framework keywords (e.g., ``Java Swing'' or ``Java SWT'')
in the above three source repositories, and then select subjects based on the following
criterias. First, the subject must be a multithread GUI application, not
an open library. Second, the subject must undergone at least two years of active development,
and is listed in the first 3 results pages based on popularity. This permits us
to exclude many pre-mature subjects that may contain obvious errors.

@@

\begin{itemize}
\Item CelerFTP~\cite{celer} and FileBunker~\cite{filebunker} are two useful
SWT desktop applications.
CelerFTP implements a simple FTP client based on Java and SWT UI library, and
FileBunker is a file backup application which uses one or more GMail accounts as its backup repository.

\Item  AnyEdit~\cite{anyedit}, FileSync~\cite{filesync}, and
EclipseRunner~\cite{eclipserunner} are three popular eclipse plugins.
AnyEdit adds several new tools to  Eclipse editors, output consoles, and main menu. 
FileSync is a file synchronisation tool to keep files outside of Eclipse projects in synchronized
with Eclipse project files. EclipseRunner extends capability of running launch configurations in Eclipse IDE.

\Item  S3dropbox~\cite{s3dropbox} and SudokuPuzzleSolver~\cite{sudokusolver}
are two Swing desktop applications. S3dropbox implements a client that allows users
to drag and drop files, which are then uploaded to their Amazon S3 accounts. SodokuPuzzleSolver
computes Sodoku solutions efficiently using mutlithreading execution.

@@

\begin{table}[t]
\begin{center}
 \fontsize{9pt}{\baselineskip}\selectfont
\hspace*{-0.2cm}
\begin{tabular}{|p{4.4cm}||c|c|c|c|}
\hline
 Program (version) & LOC & Classes & Methods \\
\hline \hline
\multicolumn{4}{|l|}{SWT desktop applications}   \\
 \hline
 CelerFTP (3.0 alpha) &  2293 &  20 &  165  \\
 \hline
 FileBunker (1.1.2)&  14237 &  150 &  1106  \\
 \hline
 \hline
\multicolumn{4}{|l|}{Eclipse plugins}   \\
 \hline
 EclipseRunner (1.1.0) &  3101 &  48 &  354\\
 \hline
 FileSync (1.4.0)&  7374 &  36 &  510 \\
 \hline
 AnyEdit (2.4.0)&  11077 &  74 &  649 \\
 \hline
 \hline
\multicolumn{4}{|l|}{Swing desktop applications}   \\
 \hline
 S3dropbox (1.7) &  2353 &  42  &  224 \\
 \hline
 Sudoku Solver (1.06)&  3555 &  10 &  62 \\
 \hline
 \hline
\multicolumn{4}{|l|}{Android mobile applications}   \\
 \hline
 SGTPuzzler (v9306.11)&  2220 &  16 &  148 \\
 \hline
 Fennec (10.0.a.rc3)&  8577 &  51 &  620 \\
 \hline
 MyTracks (1.1.13.rc4)&  20297 &  143 &  1374 \\
\hline
\multicolumn{4}{l}{}   \\
\hline
 GUI framework (version) & LOC & Classes & Methods  \\
\hline \hline
 SWT (3.6.2)&  xxxxx &  xxx &  xxxx  \\
\hline
 Eclipse plugin development (3.6.2)&  xxxxx &  xxx &  xxxx  \\
\hline
Swing (1.6)&  xxxxx &  xxx &  xxxx  \\
\hline
 Android (3.6)&  xxxxx &  xxx &  xxxx  \\
\hline
\end{tabular}

\end{center}
\vspace{-15pt}
\Caption{{\label{table:subjects} Open source programs
used in our evaluation. Column ``LOC'' is the number of lines
of code, as counted by LOCC~\cite{locc}.  Each program is analyzed
together with its dependent GUI framework, as listed in
the bottom table.} }
\end{table}

@@

We run our tool on each subject with three call graph construction
algorithms: RTA~\cite{rta}, 0-CFA, and 1-CFA~\cite{kcfa}.  When running
each call graph construction algorithm on Android applications, we
use two configurations: with and without the reflection-aware transformation
(Section~\ref{sec:cg}).  We did not use more expensive algorithms like $k$-CFA ($k >$ 1),
because they can not scale to large programs.

We inspect the source code of each subject to determine whether any
native methods or project-specific GUI interaction patterns are implemented.
We found SGTPuzzler is the only subject that uses native methods to interact with
underlying operating systems. Thus, we manually added XXX \CodeIn{@CalledByNative}
annotations for it. Also two subjects XXXX and XXX employ a self-defined
way to interact with the GUI framework. For example, the \CodeIn{safeInvokeXX}
method in the XXX subject first checks whether the current thread is the UI-thread, and
then determines whether to direct access a GUI object or wrap the code with
message passing. We add XX heuristic filtering rules for those methods, to indicate
that they are safe to be invoked from any thread. In this experiment, none of the paper
authors was faimilar with the subjects; but we found it is quite easy
to add extra those annotations and heuristic filters and finished these
manual parts in less than 20 minutes.

@@

\begin{table*}[ht]
\begin{center}
 \fontsize{9pt}{\baselineskip}\selectfont
\hspace*{-0.2cm}
\setlength{\tabcolsep}{.65\tabcolsep}
\begin{tabular}{|l||c|c|c||c|c|c||c|c|c||c|c|}
\hline
 Subject&  \multicolumn{9}{|c||}{Our Technique} & \multicolumn{2}{|c|}{The Approach in}  \\
\cline{2-10}
 Program  &  \multicolumn{3}{|c|}{RTA / reflection aware}& \multicolumn{3}{|c|}{0-CFA / reflection aware} & \multicolumn{3}{|c||}{1-CFA / reflection aware} & \multicolumn{2}{|c|}{Section~\ref{sec:straightforward}}  \\
\cline{2-12}
 & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug & \#Warning & \#Bug\\
\hline \hline
\multicolumn{12}{|l|}{SWT desktop applications}   \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
 \hline
 \hline
\multicolumn{12}{|l|}{Eclipse plugins}   \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
 \hline
 \hline
\multicolumn{12}{|l|}{Swing desktop applications}   \\
 \hline
 S3dropbox &  xxxx &  xx &  xxx & xx & xx & xx& xx & 1 & 1 & 210 & xx \\
 \hline
  Sudoku Solver&  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& 356 & xx \\
 \hline
 \hline
\multicolumn{12}{|l|}{Android mobile applications}   \\
 \hline
 xxx &  xxxx / xxxx &  xx / xxxx &  xxx / xxxx & xx /xxx & xx / xxxx  & xx / xxxx& xx / xxx & xxxx / xxx  & xxxx / xxx& xx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
\hline
\end{tabular}
\end{center}
\vspace{-15pt}
\Caption{{\label{table:results}Experimental results in finding errors
in multithreaded GUI programs. Column ``CG Size'' shows the
call graph size in terms of node number. Column ``\#Warning''
shows the number of warnings issued by our tool. Column ``\#Bug'' shows
the actual bugs found. Columns ``RTA / reflection aware '', ``0-CFA / reflection aware'',
and ``1-CFA / reflection aware'' show the results of using different
call graph construction algorithms with (before ``/'') or without (after ``/'')
taming the reflection on Android applications. In each cell of the table
for Android applications, a slash ``/'' separates the result of
using normal call graph construction algorithm and the reflection-aware
call graph construction algorithm. As a comparison, the
results of a straightforward approach (Section~\ref{sec:straightforward}) are show at the far right.} }
\end{table*}

@@

@@

\begin{table}[t]
\begin{center}
 \fontsize{9pt}{\baselineskip}\selectfont
\setlength{\tabcolsep}{.30\tabcolsep}
\hspace*{-0.2cm}
\begin{tabular}{|l||c|c|c|c|c|c|}
\hline
 Subject & Before & \#Warning & \#Warning & \#Warning & \#Warning& \#Warning \\
 Program & Filtering & $F_1$ & $F_2$ & $F_3$&$F_4$ & $F_5$\\
\hline \hline
\multicolumn{7}{|l|}{SWT desktop applications}   \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
 \hline
 xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
 \hline
 xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
 \hline
 \hline
\multicolumn{7}{|l|}{Eclipse plugins}   \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
 \hline
 xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
 \hline
 xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
 \hline
 \hline
\multicolumn{7}{|l|}{Swing desktop applications}   \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
 \hline
 xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
 \hline
 xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
 \hline
 \hline
\multicolumn{7}{|l|}{Android mobile applications}   \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
 \hline
 xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
 \hline
 xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
\hline
\end{tabular}
\end{center}
\vspace{-15pt}
\Caption{{\label{table:filters}Number of warnings after applying a set of
heuristic filters (Section~\ref{sec:heuristic}). Column ``\#Warning $F_i$''
represents the number of remaining warnings after applying
filters 1 -- $i$, and the number of last column is taken
from Table~\ref{table:results} (Subcolumn ``\#Warning'' under column ``1-CFA / with taming reflection'').} }
\end{table}

@@

The technique presented in this paper offers a promising solution.
Compared with the straightforward approach to check every
GUI accessing code isolatedly, our technique produces significantly
less warniings. The reflection-aware call graph construction algorithm
is critical in detecting errors for Android programs, and our
proposed heuristic filtering rules are useful in reducing programmers'
burden to inspect the output result.

@@

% Reporting on violations is fine but what is more important are the pracitces and patterns that need to be adopted to make it easier to avoid the issue in the first place. That is why there is a Worker interface in this project

>>>>

We use a set of open-source projects from Sourceforge, Google code and Eclipse plugin
market as evaluation subjects. To choose subjects for each supported GUI framework,
we first search the framework keywords (e.g., ``Java Swing'' or ``Java SWT'')
in the above three source repositories, and then select subjects based on the following
criterias. First, the subject must be a multithreaded GUI application, not
an open library. Second, the subject must undergone at least two years of active development,
and is listed in the first 3 results pages based on popularity. This permits us
to exclude many pre-mature subjects that may contain obvious errors.

@@

\begin{itemize}
\Item VirgoFTP~\cite{virgo} and FileBunker~\cite{filebunker} are two useful
SWT desktop applications.
VirgoFTP implements a simple FTP client based on Java and SWT UI library, and
FileBunker is a file backup application which uses one or more GMail accounts as its backup repository.

\Item  HudsonEclipse~\cite{hudson}, and
EclipseRunner~\cite{eclipserunner} are two popular eclipse plugins.
HudsonEclipse adds several new tools to  monitor Hudson build status from Eclipse.
EclipseRunner extends capability of running launch configurations in Eclipse IDE.

\Item  S3dropbox~\cite{s3dropbox} and SudokuSolver~\cite{sudokusolver}
are two Swing desktop applications. S3dropbox implements a client that allows users
to drag and drop files, which are then uploaded to their Amazon S3 accounts. SodokuSolver
computes Sodoku solutions efficiently using mutlithreading execution.

@@

\begin{table}[t]
\begin{center}
 \fontsize{9pt}{\baselineskip}\selectfont
\hspace*{-0.2cm}
\setlength{\tabcolsep}{.75\tabcolsep}
\begin{tabular}{|p{4.4cm}||c|c|c|c|}
\hline
 Program (version) & LOC & Classes & Methods \\
\hline \hline
\multicolumn{4}{|l|}{SWT desktop applications}   \\
 \hline
 VirgoFTP (1.3.5) &  2293 &  20 &  165  \\
 \hline
 FileBunker (1.1.2)&  14237 &  150 &  1106  \\
 \hline
 \hline
\multicolumn{4}{|l|}{Eclipse plugins}   \\
 \hline
 EclipseRunner (1.1.0) &  3101 &  48 &  354\\
 \hline
 HudsonEclipse(1.0.9)&  11077 &  74 &  649 \\
 \hline
 \hline
\multicolumn{4}{|l|}{Swing desktop applications}   \\
 \hline
 S3dropbox (1.7) &  2353 &  42  &  224 \\
 \hline
 SudokuSolver (1.06)&  3555 &  10 &  62 \\
 \hline
 \hline
\multicolumn{4}{|l|}{Android mobile applications}   \\
 \hline
 SGTPuzzler (v9306.11)&  2220 &  16 &  148 \\
 \hline
 Fennec (10.0.a.rc3)&  8577 &  51 &  620 \\
 \hline
 MyTracks (1.1.13.rc4)&  20297 &  143 &  1374 \\
\hline
\multicolumn{4}{l}{}   \\
\hline
 GUI framework (version) & LOC & Classes & Methods  \\
\hline \hline
 SWT (3.6)&  129942 &  999 &  9643 \\
\hline
 Eclipse plugin development (3.6.2)&  460830 &  6630 &  37183 \\
\hline
Swing (1.6)&  167961 &  878 &  13159 \\
\hline
 Android (3.2)&  683289 &  5085 &  10584 \\
\hline
\end{tabular}

\end{center}
\vspace{-15pt}
\Caption{{\label{table:subjects} Open source programs
used in our evaluation. Column ``LOC'' is the number of non-blank, non-comment lines
of code, as counted by LOCC~\cite{locc}.  Each program is analyzed
together with its dependent GUI framework, as listed in
the bottom table.} }
\end{table}

@@

We run our tool on each subject with three call graph construction
algorithms: RTA~\cite{rta}, 0-CFA, and 1-CFA~\cite{kcfa}.  When running
each call graph construction algorithm on Android applications, we
use two configurations: with and without the reflection-aware transformation
(Section~\ref{sec:cg}).  We did not use other more expensive algorithms like $k$-CFA ($k >$ 1),
because they can not scale to large programs.

We inspect the source code of each subject to determine whether any
native methods or project-specific GUI interaction patterns are implemented.
We found SGTPuzzler is the only subject that uses native methods to interact with
underlying operating systems. Thus, we manually added XXX \CodeIn{@CalledByNative}
annotations for it. Also two subjects XXXX and XXX employ a self-defined
way to interact with the GUI framework. For example, the \CodeIn{safeInvokeXX}
method in the XXX subject first checks whether the current thread is the UI-thread, and
then determines whether to direct access a GUI object or wrap the code with
message passing. We add XX heuristic filtering rules for those methods, to indicate
that they are safe to be invoked from any thread. In this experiment, none of the paper
authors was familar with the subjects; but we found it is quite easy
to add extra those annotations and heuristic filters and finished these
manual parts in less than 20 minutes.

@@

\begin{table*}[ht]
\begin{center}
 \fontsize{9pt}{\baselineskip}\selectfont
\hspace*{-0.2cm}
\setlength{\tabcolsep}{.45\tabcolsep}
\begin{tabular}{|l||c|c|c||c|c|c||c|c|c||c|c|}
\hline
 Subject&  \multicolumn{9}{|c||}{Our Technique} & \multicolumn{2}{|c|}{The Approach in}  \\
\cline{2-10}
 Program  &  \multicolumn{3}{|c|}{RTA / reflection aware}& \multicolumn{3}{|c|}{0-CFA / reflection aware} & \multicolumn{3}{|c||}{1-CFA / reflection aware} & \multicolumn{2}{|c|}{Section~\ref{sec:straightforward}}  \\
\cline{2-12}
 & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug & \#Warning & \#Bug\\
\hline \hline
\multicolumn{12}{|l|}{SWT desktop applications}   \\
 \hline
 VirgoFTP&  12401 &  2 &  2 & 10858 & 2 & 2 & 43598 & 2 & 2& 149 & 2 \\
 \hline
 FileBunker &  18951 &  1 &  0 & 15743 & 0 & 0 & 76088 & 2 & 1& 693 & 1 \\
 \hline
 \hline
\multicolumn{12}{|l|}{Eclipse plugins}   \\
 \hline
 EclipseRunner&  11248&  6 &  1 & 7201 & 6 & 1 & 26911 & 6 & 1& 202 & 1 \\
 %\hline
 %FileSync&  12132 &  xx &  xxx &8235 & xx & xx& 32565 & 1 & 1 & 331 & 1 \\
 \hline
 HudsonEclipse& 18473 &  2 &  1 & 15814 & 2 & 1& 56645 & 3 & 1 & 182 & 1 \\
 \hline
 \hline
\multicolumn{12}{|l|}{Swing desktop applications}   \\
 \hline
 S3dropbox & 37751 &  0 &  0 & 30609 & 0 & 0 & 115324 & 1 & 1 & 210 & 1 \\
 \hline
  SudokuSolver&  27730&  3 &  2 & 20907 & 3 & 2 & 39299 & 2 & 2 & 356 & 2 \\
 \hline
 \hline
\multicolumn{12}{|l|}{Android mobile applications}   \\
 \hline
 SGTPuzzler & 13631 / 13865&  12 / 16 &  0 / 0 & 9546 / 9682& 4 / 4& 1 / 1 & 35198 / 35756 & 1 / 1  & 1 / 1& 104 & 1 \\
 \hline
 Fennec & 14058 / 14387 &  55 / 54 &  0 / 0 & 8263 / 8898 & 0 / 0 & 0 / 0& 29125/ 31759 & xx / xxx & 0 / xxx& 433 & 1 \\
 \hline
 MyTracks & 24036 / 24036 &  161 / 220 & 0 / 0 & 10803 / 13645 & 119 / 119 & 0 / 0 & 39235 / 110977 & 61 / xxx & 0 / xxx& 1192 & 1 \\
\hline
\end{tabular}
\end{center}
\vspace{-15pt}
\Caption{{\label{table:results}Experimental results in finding errors
in multithreaded GUI programs. Column ``CG Size'' shows the
call graph size in terms of node number. Column ``\#Warning''
shows the number of warnings issued by our tool. Column ``\#Bug'' shows
the actual bugs found. Columns ``RTA / reflection aware '', ``0-CFA / reflection aware'',
and ``1-CFA / reflection aware'' show the results of using different
call graph construction algorithms with (before ``/'') or without (after ``/'')
taming the reflection on Android applications. In each cell of the table
for Android applications, a slash ``/'' separates the result of
using normal call graph construction algorithm and the reflection-aware
call graph construction algorithm. As a comparison, the
results of a straightforward approach (Section~\ref{sec:straightforward}) are show at the far right.} }
\end{table*}

@@

why finds a bug in SGTPuzzle, because the \CodeIn{SmallKeyBoard} has been
explicitly created in this main class \CodeIn{SGTPuzzles} \CodeIn{setKeyboardVisibility},
thus, even without reflection-aware

Why RTA, 0-CFA finds few, because they do not distinguish different
calling context.

@@

\begin{table}[t]
\begin{center}
 \fontsize{9pt}{\baselineskip}\selectfont
\setlength{\tabcolsep}{.01\tabcolsep}
\hspace*{-0.2cm}
\begin{tabular}{|l||c|c|c|c|c|c|}
\hline
 Subject & Before & \#Warning & \#Warning & \#Warning & \#Warning& \#Warning \\
 Program & Filtering & $F_1$ & $F_2$ & $F_3$&$F_4$ & $F_5$\\
\hline \hline
\multicolumn{7}{|l|}{SWT desktop applications}   \\
 \hline
 VirgoFTP &  21 &  21 &  3 & 3 &  2 & 2\\
 \hline
 FileBunker &  4494 &  3210 &  3210 &  642 &  2 & 2\\
 \hline
 \hline
\multicolumn{7}{|l|}{Eclipse plugins}   \\
 %\hline
 %EclipseRunner &  xxxx &  xx &  xxx & xx &  xxx & xx\\
 \hline
 EclipseRunner&  1621 &  1487 &  1487 & 1487 &  5 & 1\\
 \hline
 HundsonEclipse&  3192 &  2417 &  1696 & 9 &  3 & 3\\
 \hline
 \hline
\multicolumn{7}{|l|}{Swing desktop applications}   \\
 \hline
 S3dropbox&  45528 &  31978 &  30975 & 9 &  1 & 1\\
 \hline
 SudokuSolver &  58 &  58 &  58 & 2 &  2 & 2\\
 \hline
 \hline
\multicolumn{7}{|l|}{Android mobile applications}   \\
 \hline
 SGTPuzzler&  2 &  1 &  1 & 1 &  1 & 1\\
 \hline
 Fennec &  xxxx &  xx &  xxx & xx &  xxx & xx\\
 \hline
 MyTracks &  xxxx &  xx &  xxx & xx &  xxx & xx\\
\hline
\end{tabular}
\end{center}
\vspace{-15pt}
\Caption{{\label{table:filters}Number of warnings after applying a set of
heuristic filters (Section~\ref{sec:heuristic}). Column ``Before Filtering''
shows the output warning number using the reflection-aware 1-CFA algorithm.
Column ``\#Warning $F_i$'' represents the number of remaining warnings after applying
filters 1 -- $i$, and the number in last column is taken
from Table~\ref{table:results}.
Results of using other algorithms show similar patterns, which are omitted for brevity.} }
\end{table}

@@

The technique presented in this paper offers a promising solution.
Compared with the straightforward approach to check every
GUI accessing code isolatedly, our technique produces significantly
less warnings. The reflection-aware call graph construction algorithm
is critical in detecting errors for Android programs, and our
proposed heuristic filtering rules are useful in reducing programmers'
burden to inspect the output result.

@@

% Reporting on violations is fine but what is more important are the practices and patterns that need to be adopted to make it easier to avoid the issue in the first place. That is why there is a Worker interface in this project

### 2012-01-26 trunk/GUIErrorDetector/paper/introduction.tex
revise implementation and evaluation sections
revise

\section{Introduction}

@@

Many popular GUI frameworks such as Swing\footnote{\url{http://docs.oracle.com/javase/6/swing/}},
SWT\footnote{\url{http://eclipse.org/swt/}}, Android\footnote{\url{http://www.android.com/}},
Qt\footnote{\url{http://qt.nokia.com/products/}}, MacOS Cocoa\footnote{\url{http://developer.apple.com/cocoa.html}},
and X Windows\footnote{\url{http://www.x.org/}}
adapt the \textit{single-thread rule}:

@@

Take the popular Standard Widget Toolkit (SWT) GUI framework as an example. 
The invalid thread access error is one of the top 3 bugs in developing a SWT application, and is
the source of many relevant concurrency bugs~\footnote{\url{http://www.slideshare.net/lakshmip/top-3-swt-exceptions-3951224}}.
A Google search for ``SWTException:Invalid thread access''  returns over 11,800 entries,
consisting of numerous bug reports, forum posts, and mailing list threads on
this problem. Eclipse, the IDE for Java development, is built on top of SWT.
Searching for ``SWTException:Invalid thread access'' in Eclipse's bug repository
and discussion forum returns over 2732 bug reports and 351 distinct threads, respectively. 
We manually studied all 156 \textit{confirmed} distinct bug reports, and 
found this error has been reported in at least 20 distinct eclipse projects
and 40 distinct eclipse components. Even after over 10 years of active development,
a recent release of Eclipse still contains this error (bug id: 333533, reported in 01/2011).
 Furthermore, many reported  errors are non-trivial, and it is unintuitive
to fix them. Developers usually need non-local reasoning to find the specific
UI interactions that can trigger the bug;  it even took developers 2 years
to fix bug: 51757 and verify the patch. In addition, the invalid thread access error
is UI-relevant and user-perceivable; it cannot be recovered by the program itself
and often terminates the whole application. In many circumstances as described in the bug reports,
users can only restart the application to recover from the error.

@@

\subsection{Finding Invalid Thread Access Errors}

@@

%Program refactoring~\cite{Mens:2004}, another popular way to improve software quality,
%is also inadequate to eliminate this error. 
A standard way to fix an
invalid thread access error is to replace direct GUI object accessing code 
with asynchronized message passing, to ensure a GUI object are accessed in
the UI thread. For example, to fix the bug in Figure~\ref{fig:androiderror},
a developer would wrap line 222 inside a \CodeIn{post} message passing method\footnote{The
\CodeIn{post} method in class \CodeIn{android.widget.View} is a
a standard way to send messages to the UI-thread.}, as follows:

@@

One may wonder that a straightforward program transformation to wrap
every possible UI-accessing operation with asynchronized message passing
may avoid the invalid thread error. However, such an approach is problematic,
because using asynchronized message passing has no timing
guarantee. It is entirely possible that, in some cases, a GUI object has already been
disposed before the message sent to arrives, causing other bugs. Thus, programmers can not use
it everywhere; instead, they must choose carefully to put it in appropriate places
with extreme caution. This makes invalid thread errors even harder to avoid,
and demands a proactive technique to detect them.

@@

Our static analysis is independent of the call graph construction algorithms.
Given a sound call graph, our analysis is sound in that it does
not miss true positives. We note, however, that computing a sound
call graph with acceptable precision for GUI applications in the presence of reflection
is non-trivial.
Existing call graph construction algorithms such as RTA~\cite{} and k-CFA~\cite{}
either suffer from either imprecision or incompleteness .
To alleviate this problem,
we present a combined RTA and k-CFA call graph construction algorithm, and
also compare its usefulness with other algorithms in  our experiments. We
also note that static analysis may report false positives due to its
conservative nature, or multiple warnings that actually correspond
to the same error. To alleviate such limitations, we devise a set
 of heuristics to filter likely false positives and redundant warnings.

@@

We instantiated our technique for popular four GUI frameworks namely SWT,
eclipse plugin environment, Java Swing, and Android. 
Swing and SWT are unquestionably 
two dominating GUI frameworks in developing desktop Java applications.
Eclipse with its plugin development envrionment is the de-facto standard
IDE for Java. Android is the No. 1 platform for
developing mobile applications with market share 56\% as of Sep 2011.
Although our technique is generally applicable for GUI
frameworks adapting the single-thread rule, a specific framework
may have its own treatment of \textit{UI thread} and \textit{call graph
entry nodes}. Thus, we must explicitly identify those framework-specific
parts in our prototype tool implementation.

@@

We implement an invalid thread error detection tool that supports
the above four GUI frameworks. Our tool works in a fully-automatic,
push-button manner, and scales to realistic programs.
We evaluate our implementation on XXX subjects from four different
frameworks over XXX LOC. The experiment results demonstrate
that: our technique is effective (it found XXX real-world errors
on all supported frameworks); our combined RTA and k-CFA call
graph construction algorithm is useful (XXX it improves both completeness
and precision over the existing algorithms), and our proposed
heuristics are useful (it signficantly reduces the number of
false positives and redundant warnings).

@@

\item \textbf{Evaluation.} We performed an experiment on XXX subjects
from 4 different platforms over XXX LOC to show the usefulness
of the proposed techinque (Section~\ref{sec:evaluation}).

>>>>

\section{Introduction}
\label{sec:introduction}

@@

Many popular GUI frameworks such as Swing~\cite{swing},
SWT~\cite{swt}, Android~\cite{android},
Qt~\cite{qt}, MacOS Cocoa~\cite{macos},
and X Windows~\cite{xwindow}
adapt the \textit{single-thread rule}:

@@

Take the popular Standard Widget Toolkit (SWT) GUI framework as an example. 
The invalid thread access error is one of the top 3 bugs in developing a SWT application, and is
the source of many relevant concurrency bugs~\cite{top3bugs}.
A Google search for ``SWTException:Invalid thread access''  returns over 11,800 entries,
consisting of numerous bug reports, forum posts, and mailing list threads on
this problem. Eclipse, the IDE for Java development, is built on top of SWT.
Searching for ``SWTException:Invalid thread access'' in Eclipse's bug repository
and discussion forum returns over 2732 bug reports and 351 distinct threads, respectively. 
We manually studied all 156 \textit{confirmed} distinct bug reports, and 
found this error has been reported in at least 20 distinct eclipse projects
and 40 distinct eclipse components. Even after over 10 years of active development,
a recent release of Eclipse still contains this error (bug id: 333533, reported in 01/2011).
 Furthermore, many reported  errors are non-trivial, and it is unintuitive
to fix them. Developers usually need non-local reasoning to find the specific
UI interactions that can trigger the bug;  it even took developers 2 years
to fix bug: 51757 and verify the patch. In addition, the invalid thread access error
is UI-relevant and user-perceivable; it cannot be recovered by the program itself
and often terminates the whole application. In many circumstances as described in the bug reports,
users can only restart the application to recover from the error.

@@

\subsection{Finding Invalid Thread Access Errors}
\label{sec:finding}

@@

%Program refactoring~\cite{Mens:2004}, another popular way to improve software quality,
%is also inadequate to eliminate this error.

%One way to find such invalid thread access error is to check every GUI object
%accessing code to see whether

A standard way to fix an
invalid thread access error is to replace direct GUI object accessing code 
with asynchronized message passing, to ensure a GUI object is accessed in
the UI thread. For example, to fix the bug in Figure~\ref{fig:androiderror},
a developer would wrap line 222 inside a \CodeIn{post} message passing method\footnote{The
\CodeIn{post} method in class \CodeIn{android.widget.View} is a
a standard way to send messages to the UI-thread.}, as follows:

@@

One may wonder that a simple analysis to check whether every GUI object
accessing code has been wrapped by (a)synchronized message passing may
be capable to find invalid thread errors. However, such an approach is problematic,
because not every GUI object access needs to be wrapped by a message passing
method, e.g., methods that are only called from UI-thread can safely
access any GUI object. On the other hand, using asynchronized message passing has no timing
guarantee. It is entirely possible that, in some cases, a GUI object has already been
disposed before the message sent to arrives, causing other bugs. 
Thus, programmers can not use it everywhere to wrap all GUI object accessing code.
In our evaluation on real world programs, we found this simple analysis 
can not be used in practice: it issued
an unacceptable number of false positives and redundant warnings.

%program transformation to wrap
%every possible UI-accessing operation with asynchronized message passing
%may avoid the invalid thread error. However, such an approach is problematic,
%because using asynchronized message passing has no timing
%guarantee. It is entirely possible that, in some cases, a GUI object has already been
%disposed before the message sent to arrives, causing other bugs. Thus, programmers can not use
%it everywhere; instead, they must choose carefully to put it in appropriate places
%with extreme caution. This makes invalid thread errors even harder to avoid,
%and demands a proactive technique to detect them.

@@

Our static analysis is independent of the call graph construction algorithms.
Given a sound call graph, our analysis is sound in that it does
not miss true positives. We note, however, that computing a sound
call graph with acceptable precision for GUI applications in the presence of reflection
is non-trivial.
Existing call graph construction algorithms such as RTA~\cite{rta}
and k-CFA~\cite{kcfa}
fails to build a sufficiently complete call graph, due to their limitations
to reason about reflections.  To alleviate this problem,
we present a method to build reflection-aware call graph, and
also compare its usefulness with existing call graph construction algorithms in
our experiments. We also note that static analysis may report false positives due to its
conservative nature, or multiple warnings that actually correspond
to the same error. To alleviate such limitations, we devise a set
 of heuristics to filter likely false positives and redundant warnings.

@@

We instantiated our technique for four popular GUI frameworks namely SWT,
eclipse plugin environment, Java Swing, and Android. 
Swing and SWT are unquestionably 
two dominating GUI frameworks in developing desktop Java applications.
Eclipse and its plugin development environment is the de-facto standard
IDE for Java. Android is the No. 1 platform for
developing mobile applications with market share 56\% as of Sep 2011.
Although our technique is generally applicable for GUI
frameworks adapting the single-thread rule, a specific framework
may have its own treatment of \textit{UI thread} and \textit{call graph
entry nodes}. Thus, we must explicitly identify those framework-specific
parts in our prototype tool implementation.

@@

We implement an invalid thread error detection tool that supports
the above four GUI frameworks. Our tool works in a fully-automatic,
push-button manner, and scales to realistic programs.
We evaluate our implementation on 10 subjects from four different
frameworks over 75000 LOC. The experiment results demonstrate
that: our technique is effective (it found 12 real-world errors
on all supported frameworks, and produced significantly less
false positives and redundant warnings than the simple analysis);
our reflection-aware call graph construction algorithm is
critical in finding errors in Android applications,
and our proposed
heuristics are useful (it significantly reduces the number of
false positives and redundant warnings).

@@

\item \textbf{Evaluation.} We performed an experiment on 10 subjects
from 4 different platforms over 75000 LOC to show the usefulness
of the proposed technique (Section~\ref{sec:evaluation}).
